Multisensor Architecture for an Intersection Management System

### 2019-01-22 ch3-arch_sys.tex
Fixed JSON description and Information structure (2.3.3) and Fixed formatting in section 2.3.4

Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options. This information is loaded into Redis from a JSON file and it is available for any client requiring it.
\todo{Define JSON HERE!!!!}

@@

The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to. For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{"laser\_1"} and \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{leg\_3}.

@@

\todo{Move JSON definition from here!!!}
Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JavaScript Object Notation (JSON), allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.

@@

\begin{description}

@@

\subsubsection{Situation Assesment}

>>>>

Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options. This information is loaded into Redis from a configuration file formatted using JavaScript Object Notation (JSON), and once loaded in Redis, it is available for any client requiring it.
\todo{Define JSON HERE!!!!}

@@

The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where data is generated from or where data is going to. For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{"laser\_1"} and \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{leg\_3}.

@@

\todo{Move JSON definition from here!!!}
Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JSON, allowing to use any JSON parser/formatter available in different languages. In addition,  it is possible to create simple scripts to interact with the system. Below are described the two types of data used by the systems: the .imscfg file and the messages and configuration parameters.

@@

@@

\subsubsection{Situation Assesment}
\begin{description}
